---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/Curious-Joe/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Curious-Joe/ussie/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ussie is to prepare data provided by the package `{engsoccerdata}` in a consistent data frame format. 

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Curious-Joe/ussie")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ussie)

## basic example code
spain <- uss_make_matches(engsoccerdata::spain, "Spain")
head(spain)

```

The above example should,

* Fetch the data about Spain from the `engsoccerdata` package
* Process it into a consistently formatted `tibble`
* Finally using `head()` function show top 10 rows of the tibble.

*** 

## Document Details

Prepared By: Arafath Hossain

Date: July 25th, 2022
